\documentclass{article}
\usepackage{geometry}
\usepackage{verbatim}
\geometry{letterpaper, margin=0.5in}
\usepackage{enumitem}
\setlist{nolistsep}
\pagenumbering{gobble}


\begin{document}
\begin{center}
	\noindent\rlap{\huge\textbf{\centerline{Jeremy J. Kerby}}}\rule[-2pt]{\textwidth}{.5pt}
	\normalsize{e: jjkerby@dons.usfca.edu | c: +1(650)722-0144 | GitHub: /jeremyjkerby | LinkedIn: /jeremyjkerby}
\end{center}


\noindent\rlap{\large\textbf{\centerline{EDUCATION}}}\rule[-2pt]{\textwidth}{.3pt}
\noindent\large{\textbf{University of San Francisco}}
\normalsize{
	\hspace*{340pt}May 2018\\
	\hspace*{20pt}\textbf{B.S.} in Computer Science, \textbf{Minor} in Chinese Studies\\
	\hspace*{20pt}\textbf{GPA:} 3.54, \textbf{Honors:} Cum Laude, USF Dean's List\\
	\hspace*{20pt}\textbf{Relevant Courses:} Systems Foundations (Graduate Course, C/ARM Assembly), Senior Team Project, Operating Systems, Data Structures and Algorithms, Parallel/C Programming, Software Development OOP}

\noindent\large{\textbf{Santa Barbara City College}}\\
\normalsize{
	\hspace*{20pt}\textbf{A.S.} in Computer Science, \textbf{A.A.} in Science and Math\\
}


\noindent\rlap{\large\textbf{\centerline{EXPERIENCE}}}\rule[-2pt]{\textwidth}{.3pt}
\noindent\large{\textbf{Senior Team Project - Python}}\\
\normalsize{
	\textit{University of San Francisco, San Francisco, CA}\hspace*{200pt}August 2017 - December 2017\\
	\vspace{-4mm}
		\begin{itemize}
  			\item Worked with a top industry partner, Twitter, Inc. to develop a sophisticated Python application.
  			\item Front-end was written in JavaScript, back-end was written in Python, data was stored in a MySQL database. Application utilized multi-window user interface, thousands of rows of data, and communicated with a third-party API.
  			\item Elected team lead of a group of four students. Responsible for communicating directly with project sponsor to gather ambiguous complex requirements as well as provide feedback to the team.
  			\item Won best team award by faculty.
		\end{itemize}
}
\noindent\large{\textbf{Instructional Student Assistant - CS/Math}}\\
\normalsize{
	\textit{CSU Channel Islands, Camarillo, CA}\hspace*{270pt}August 2015 - May 2016\\
	\vspace{-4mm}
		\begin{itemize}
			\item Worked as an on campus tutor in a community of diverse students in a one on one or group setting.
			\item Provided tutoring in computer science courses; Data Structures, OOP, MySQL, MS Office.
			\item Provided tutoring in math courses; Calculus II, Calculus I, Linear Algebra, Algebra, Geometry.
			\item Paid position to work directly with a math professor as a homework grader for a Calculus I class.
			\item Note: Transferred to USF
		\end{itemize}
}
\noindent\large{\textbf{Software QA Engineer}}\\
\normalsize{
	\textit{Invoca, Santa Barbara, CA}\hspace*{305pt}January 2014 - March 2015\\
	\vspace{-4mm}
		\begin{itemize}
			\item Developed and executed usability as well as behavioral test plans covering a wide array of edge cases.
			\item Investigated and analyzed issues facing the enterprise suite. Created and tracked issues on Jira.
			\item Collaborated with my scrum team members on a daily basis to communicate detailed information about current issues.
			\item Extensively utilized tools such as Jira and Trello to track issues, Slack to communicate with the team, and Github to investigate issues in the code base.\\
		\end{itemize}
}


\noindent\rlap{\large\textbf{\centerline{PASSION PROJECTS}}}\rule[-2pt]{\textwidth}{.3pt}\\
\noindent\large{\textbf{Cardio Buddy}}\\
\normalsize{
	\textit{https://github.com/jeremyjkerby/CardioBuddy}\hspace*{237pt}Status: In Development\\
	\vspace{-4mm}
		\begin{itemize}
			\item Allow Android users to track cardio workouts and have ability to backup their information to a Python server.
			\item Python server built with Flask framework, MySQL database, and provides custom built API to communicate with multiple Android devices.
  			\item Android application utilizes multi-window user interface, stores data locally on user devices using SQLite, and communicates with a headless server via a custom built API.\\
		\end{itemize}
}


\noindent\rlap{\large\textbf{\centerline{COMPUTER SKILLS}}}\rule[-2pt]{\textwidth}{.3pt}\\
\normalsize{
	Languages: Python, Java, JavaScript, PHP, C\\
	Databases: MySQL, MySQL Workbench\\
	Additional: Git, Vim, OSX, Windows, RESTful API, Jira, Slack, Google Suite, Microsoft Office (Word, PowerPoint, Excel), Agile Development, Scrum\\
	Personal: time management, detail oriented, problem solver, communicative, collaborative, energetic, passionate\\
}


\noindent\rlap{\large\textbf{\centerline{INTERESTS}}}\rule[-2pt]{\textwidth}{.3pt}\\
\normalsize{cold-brew, hot-pot, cooking, hiking, running, Android, TechCrunch, Wired, HackerRank}

\end{document}
